Group B Analysis

### 2021-05-30 group-b/group-b-analysis.Rmd
update plot

ggplot(rt.summary.condition.data, aes(x=relation, fill=condition, color=condition, y=M, ymax=M+SE, ymin=M-SE, group=condition))+
  geom_point(size=5)+
  geom_line()+
  geom_errorbar(width=0.2)+
  scale_color_manual(values=c("orange2","royalblue4"))+
  labs(x="Statement Type", y="Accuracy", color=NULL)+
  theme_classic()
```

>>>>

ggplot(rt.summary.condition.data, aes(x=relation, color=condition, y=M, ymax=M+SE, ymin=M-SE, group=condition))+
  geom_point(size=5)+
  geom_line()+
  geom_errorbar(width=0.2)+
  scale_color_manual(values=c("orange2","royalblue4"))+
  labs(x="Statement Type", y="Response Time (ms)", color=NULL)+
  theme_classic()
```
